### 2016-03-18 text/MS.Rmd
first version submitted to Functional Ecology

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
load('../output/RDatafiles/analyses.RData')
load('../output/RDatafiles/numbers.RData')
source('../R/functions-analyses.R')
source('../R/functions-figures.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=TRUE)
```
**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

Diego R. Barneche, Craig R. White, Dustin J. Marshall

Centre for Geometric Biology / School of Biological Sciences, Monash University, Clayton, Victoria, Australia 3800

@@

Our model selection approach indicated that the three-way interaction model (equation 2) performed significantly better than all nested two- and one-way interaction models (Table 2), thus implying that different species present different interactions between mass-scaling and temperature dependence. Particularly, the best model yields no interaction between mass scaling and temperature dependence for *Bugula stolonifera* and the Microcionidae sponge (large overlap between 95\% credible intervals for the mass-scaling slopes, $\alpha$) (Figure 1). Still, while the mass-scaling slopes are statistically the same between temperatures for these species, there is evidence for higher metabolic normalisations (i.e. intercepts), $B_o$, at higher temperatures (though not statistically significant for Microcionidae). For example, metabolic rates increase `r rounded(exp(averageEstimates$lnB25[averageEstimates$species == 'Stolonifera'])/exp(averageEstimates$lnB10[averageEstimates$species == 'Stolonifera']))`-fold between 10 ˚C and 25 ˚C for *B. stolonifera*, yielding a $Q_{10}$ of `r rounded(q10andErs$q10[q10andErs$species == 'Stolonifera'])`, which is equivalent to an activation energy of `r rounded(q10andErs$er[q10andErs$species == 'Stolonifera'], 2)` eV `r myCite(c('gillooly2001','yvondurocher2012a'))`. The best model indicates that the difference in metabolic rates between 25 ˚C and 10 ˚C for *Hippopodina* sp. decreases, on average, `r rounded(tempDeltas[1,'tempDelta'])`-fold moving from `r round(exp(2))` to `r round(exp(5))` mg. For *Bugula neritina*, however, rates increase `r rounded(1/tempDeltas[3,'tempDelta'])`-fold along the same body-mass gradient.

@@

At the population level, disturbance and predation can also create different size distributions. Our finding of allometric scaling of metabolic rate implies non-intuitive outcomes of such shifts in mean size of colonies in a population. For example, at 25 ˚C a population of 10 colonies of *Bugula neritina* that each weigh 10 mg would have a cumulative metabolic demand of `r rounded(10 * exp(averageEstimates$lnB25[averageEstimates$species == 'Bugula'] + log(10)*averageEstimates$s25[averageEstimates$species == 'Bugula']), 2)` $\mu$l $\textrm{O}_\textrm{2}$ h^-1^. If a disturbance event halved each colony with minimal loss of biomass, then a population of those (now) 20 colonies, each weighing 5 mg, would have cumulative metabolic demand of `r rounded(20 * exp(averageEstimates$lnB25[averageEstimates$species == 'Bugula'] + log(5)*averageEstimates$s25[averageEstimates$species == 'Bugula']), 2)` $\mu$l $\textrm{O}_\textrm{2}$ h^-1^ according to their new size. Thus, disturbance events change not only the size distribution of colonies but also the energy requirements of the population even if total standing biomass remains unchanged `r myCite('barneche2014ele')`.

@@

We thank the Australian Research Council for financial support (grants DP0987626, DP110101776, FT130101493 to C. R. White, and DP110103529 to DJM).

>>>>

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
load('../output/RDatafiles/analyses.RData')
load('../output/RDatafiles/numbers.RData')
source('../R/functions-analyses.R')
source('../R/functions-figures.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=FALSE)
```
**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

Diego R. Barneche\*, Craig R. White, Dustin J. Marshall

Centre for Geometric Biology / School of Biological Sciences, Monash University, Clayton, Victoria, Australia 3800  
\*Corresponding author: barnechedr@gmail.com

@@

Our model selection approach indicated that the three-way interaction model (equation 2) performed significantly better than all nested two- and one-way interaction models (Table 2), thus implying that different species present different interactions between mass-scaling and temperature dependence. Particularly, the best model yields no interaction between mass scaling and temperature dependence for *Bugula stolonifera* and the Microcionidae sponge (large overlap between 95\% credible intervals for the mass-scaling slopes, $\alpha$) (Fig. 1). Still, while the mass-scaling slopes are statistically the same between temperatures for these species, there is evidence for higher metabolic normalisations (i.e. intercepts), $B_o$, at higher temperatures (though not statistically significant for Microcionidae). For example, metabolic rates increase `r rounded(exp(averageEstimates$lnB25[averageEstimates$species == 'Stolonifera'])/exp(averageEstimates$lnB10[averageEstimates$species == 'Stolonifera']))`-fold between 10 ˚C and 25 ˚C for *B. stolonifera*, yielding a $Q_{10}$ of `r rounded(q10andErs$q10[q10andErs$species == 'Stolonifera'])`, which is equivalent to an activation energy of `r rounded(q10andErs$er[q10andErs$species == 'Stolonifera'], 2)` eV `r myCite(c('gillooly2001','yvondurocher2012a'))`. The best model indicates that the difference in metabolic rates between 25 ˚C and 10 ˚C for *Hippopodina* sp. decreases, on average, `r rounded(tempDeltas[1,'tempDelta'])`-fold moving from `r round(exp(2))` to `r round(exp(5))` mg. For *Bugula neritina*, however, rates increase `r rounded(1/tempDeltas[3,'tempDelta'])`-fold along the same body-mass gradient.

@@

At the population level, disturbance and predation can also create different size distributions. Our finding of allometric scaling of metabolic rate implies non-intuitive outcomes of such shifts in mean size of colonies in a population. For example, at 25 ˚C a population of 10 colonies of Microcionidae that each weigh 400 mg would have a cumulative metabolic demand of ~`r rounded(10 * exp(averageEstimates$lnB25[averageEstimates$species == 'Sponge'] + log(400)*averageEstimates$s25[averageEstimates$species == 'Sponge']), 0)` $\mu$l $\textrm{O}_\textrm{2}$ h^-1^. If a disturbance event halved each colony with minimal loss of biomass, then a population of those (now) 20 colonies, each weighing 200 mg, would have cumulative metabolic demand that is `r rounded((round(20 * exp(averageEstimates$lnB25[averageEstimates$species == 'Sponge'] + log(200)*averageEstimates$s25[averageEstimates$species == 'Sponge']))) / (round(10 * exp(averageEstimates$lnB25[averageEstimates$species == 'Sponge'] + log(400)*averageEstimates$s25[averageEstimates$species == 'Sponge']))), 1)`-fold higher (i.e. ~`r rounded(20 * exp(averageEstimates$lnB25[averageEstimates$species == 'Sponge'] + log(200)*averageEstimates$s25[averageEstimates$species == 'Sponge']), 0)` $\mu$l $\textrm{O}_\textrm{2}$ h^-1^), according to their new size. Thus, disturbance events change not only the size distribution of colonies but also the energy requirements of the population even if total standing biomass remains unchanged `r myCite('barneche2014ele')`.

@@

We thank the Australian Research Council for financial support (grants DP0987626, DP110101776, FT130101493 to C. R. White, and DP110103529 to D. J. Marshall). The authors declare no conflict of interest.

**Data Accessibility**

The dataset associated with this manuscript will be archived on DRYAD should the manuscript be accepted. All data and code necessary to reproduce this paper, its analyses, tables and figures can also be obtained on GitHub https://github.com/dbarneche/MTRBrEs.

### 2016-03-18 text/coverLetter.Rmd
first version submitted to Functional Ecology

Diego R. Barneche  
School of Biological Sciences  
Monash University  
Melbourne 3800 VIC  
Australia  
barnechedr@gmail.com

March XX, 2016

@@

In this article, we use a manipulative approach to test for an association between metabolic mass scaling and temperature dependence in four species of colonial marine invertebrates belonging to two phyla. By adopting a size-manipulation approach, we achieved a more definitive test of mass-scaling of metabolic rates for cancelling the confounding effects of size and age, and by mimicking predation, which constitutes a fundamental ecological process in the wild. Our results indicate that mass scaling and temperature dependence of metabolic rates interact in different ways across the studies species, and these interactions are not consistent across growth form nor phyla.

@@

Diego R. Barneche

>>>>

March 18 2016

@@

In this article, we use a manipulative approach to test for an association between metabolic mass scaling and temperature dependence in four species of colonial marine invertebrates belonging to two phyla. By adopting a size-manipulation approach, we achieved a more definitive test of mass-scaling of metabolic rates for cancelling the confounding effects of size and age, and by fragmenting colonies, a natural source of size variation in modular organisms in the wild. Our results indicate that mass scaling and temperature dependence of metabolic rates interact in different ways across the studies species, and these interactions are not consistent across growth form nor phyla.

@@

Diego R. Barneche  
(on behalf of all coauthors)  
School of Biological Sciences  
Monash University  
Melbourne 3800 VIC  
Australia  
barnechedr@gmail.com
